\begin{thebibliography}{99}
    \bibitem{LiDAR-based Person Re-identification}
    Wenxuan Guo, Zhiyu Pan, Yingping Liang, Ziheng Xi,
    Zhicheng Zhong, Jianjiang Feng, Jie Zhou,
    LiDAR-based Person Re-identification, 
    In Proceedings of the IEEE/CVF Conference on Computer Vision 
    and Pattern Recognition, pages 17437–17447, 2024.

    \bibitem{Using Boosted Features for the Detection of People in 2D Range Data}
    Kai O. Arras, \'Oscar Mart\'inez Mozos, Wolfram Burgard, 
    Using Boosted Features for the Detection of People in 2D Range Data, 
    IEEE International Conference on Robotics and Automation, 
    pages 3402–3407, 2007

    \bibitem{Online learning for 3D LiDAR-based human detection: experimental 
    analysis of point cloud clustering and classification methods}
    Zhi Yan, Tom Duckett, Nicola Bellotto, 
    Online learning for 3D LiDAR-based human detection: experimental 
    analysis of point cloud clustering and classification methods, 
    Autonomous Robotics, vol 44, pages 147–164, 2020.

    \bibitem{Monocular Person Tracking and Identification with On-line Deep 
    Feature Selection for Person Following Robots}
    Kenji Koide, Jun Miura, Emanuele Menegatti, 
    Monocular Person Tracking and Identification with On-line Deep Feature 
    Selection for Person Following Robots, 
    Robotics and Autonomous Systems, vol 124, 2020.

    \bibitem{PointPillars: Fast Encoders for Object Detection from Point Clouds}
    Alex H. Lang, Sourabh Vora, Holger Caesar, Lubing Zhou, Jiong Yang,
    Oscar Beijbom, 
    PointPillars: Fast Encoders for Object Detection from Point Clouds, 
    In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern 
    Recognition, pages 12697–12705, 2019.

    \bibitem{Are we ready for autonomous driving? the KITTI vision benchmark suite}
    Andreas Geiger, Philip Lenz, and Raquel Urtasun, 
    Are we ready for autonomous driving? the KITTI vision benchmark suite,
    In Proceedings of the IEEE/CVF Conference on Computer Vision 
    and Pattern Recognition, 2012.

    \bibitem{3D BAT: A Semi-Automatic, Web-based 3D Annotation Toolbox for 
    Full-Surround, Multi-Modal Data Streams}
    Walter Zimmer, Akshay Rangesh and Mohan Trivedi, 
    3D BAT: A Semi-Automatic, Web-based 3D Annotation Toolbox for 
    Full-Surround, Multi-Modal Data Streams,
    IEEE Intelligent Vehicles Symposium (IV), 2019.

    \bibitem{TPT-Bench: A Large-Scale, Long-Term and Robot-Egocentric Dataset for 
    Benchmarking Target Person Tracking}
    Hanjing Ye, Yu Zhan, Weixi Situ, Guangcheng Chen, Jingwen Yu, Ziqi Zhao, 
    Kuanqi Cai, Arash Ajoudani, Hong Zhang,
    TPT-Bench: A Large-Scale, Long-Term and Robot-Egocentric Dataset for 
    Benchmarking Target Person Tracking,
    arXiv, 2025.

    \bibitem{JRDB-PanoTrack: An Open-world Panoptic Segmentation and Tracking 
    Robotic Dataset in Crowded Human Environments}
    Roberto Martín-Martín, Mihir Patel, Hamid Rezatofighi, Abhijeet Shenoi, 
    JunYoung Gwak, Eric Frankel, Amir Sadeghian, Silvio Savarese,
    In Proceedings of the IEEE/CVF Conference on Computer Vision
    and Pattern Recognition, pages 22325-22334, 2024.

    \bibitem{RobSense: A Robust Multi-modal Foundation Model for Remote Sensing 
    with Static, Temporal, and Incomplete Data Adaptability}
    Minh Kha Do, Kang Han, Phu Lai, Khoa T. Phan, Wei Xiang,
    In Proceedings of the IEEE/CVF Conference on Computer Vision
    and Pattern Recognition, pages 7427-7436, 2025.

\end{thebibliography}
